Declarative Deployment Reconfiguration of Pulverised Collective Adaptive Systems at Runtime \thanks{ This work has been supported by the Italian PRIN Project COMMON-WEARS (2020HCWWLP) and the EU/MUR FSE REACT-EU PON R\&I 2014-2020. }

### 2023-05-17 paper-2023-acsos-pulverization.tex
Add simulation charts]

>>>>

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=100.0.pdf}
    \end{minipage}
    \caption{
        Results of the simulation with 100 devices.
        %
        The \emph{green} bar represents the mean power consumed by cloud;
        the \emph{blue} bar represents the mean power consumed by all the devices in the system;
        the \emph{yellow} bar represents the mean traveled distance by the people
        and the \emph{purple} bar represents the average cost per hour of the cloud.
        %
        The chart shows two ``static'' scenarios: \emph{device-only} (on the left) and \emph{cloud-only} (on the right).
        %
        All the intermediate scenarios are obtained by exploiting the reconfiguration capabilities of the pulverization framework,
        where different battery threshold are used to trigger the reconfiguration.
    }
    \label{fig:result-100-devices}
\end{figure}

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=300.0.pdf}
    \end{minipage}
    \caption{
        Results of the simulation with 300 devices.
        %
        The \emph{green} bar represents the mean power consumed by cloud;
        the \emph{blue} bar represents the mean power consumed by all the devices in the system;
        the \emph{yellow} bar represents the mean traveled distance by the people
        and the \emph{purple} bar represents the average cost per hour of the cloud.
        %
        The chart shows two ``static'' scenarios: \emph{device-only} (on the left) and \emph{cloud-only} (on the right).
        %
        All the intermediate scenarios are obtained by exploiting the reconfiguration capabilities of the pulverization framework,
        where different battery threshold are used to trigger the reconfiguration.
    }
    \label{fig:result-300-devices}
\end{figure}

\begin{figure}[ht]
    \begin{minipage}{\columnwidth}
        \includegraphics[width=\linewidth]{figures/cloud_cost-device_consumption-cloud_consumption-distance-device=1000.0.pdf}
    \end{minipage}
    \caption{
        Results of the simulation with 1000 devices.
        %
        The \emph{green} bar represents the mean power consumed by cloud;
        the \emph{blue} bar represents the mean power consumed by all the devices in the system;
        the \emph{yellow} bar represents the mean traveled distance by the people
        and the \emph{purple} bar represents the average cost per hour of the cloud.
        %
        The chart shows two ``static'' scenarios: \emph{device-only} (on the left) and \emph{cloud-only} (on the right).
        %
        All the intermediate scenarios are obtained by exploiting the reconfiguration capabilities of the pulverization framework,
        where different battery threshold are used to trigger the reconfiguration.
    }
    \label{fig:result-1000-devices}
\end{figure}
